\vspace{60pt}\\ \huge \bfseries SKEDGE \\ \vspace{10pt} \Large Smarter course scheduling for our\\ University of Rochester

### 2016-04-10 design.tex
multischedule stuff

Skedge solves this by hyperlinking each course mention to a search query for its respective course, in the style of Wikipedia. Moreover, it protects users from a context-switch by displaying a lightweight popover with that course's information when the user hovers their cursor over the course mention (see Figure \ref{fig:sk-hover}).

\begin{figure}[ht]
  \centering
  \vspace{10pt}
  \fbox{
    \includegraphics[width=8cm]{images/skedge/hover}
  }
  \caption{Hoverable and clickable course mention in the \emph{Prerequisites} field of a course} \label{fig:sk-hover}
\end{figure}

@@

- Old CDCS+betterCDCS system can't keep track of this, have conflicts when adding stuff
- Multiple schedules per semester (for different schedule possibilities)

\subsection{Exporting}

to Google Calendar, {\tt .ics}, image

- Mobile sync support
- Export gcal is currently broken
- Security: BetterCDCS ``sign in'' sends netID in PLAINTEXT over http(!!!)

@@

\subsubsection{Left side}

@@

\subsubsection{Right side}

>>>>

Skedge solves this by linking each course mention to its search query, in the style of Wikipedia. Moreover, it prevents context-switches by displaying a popover containing information on that course when the user hovers their cursor over the course mention (see Figure \ref{fig:sk-hover}).

\begin{figure}[ht]
  \centering
  \vspace{2pt}
  \fbox{
    \includegraphics[width=8cm]{images/skedge/hover}
  }
  \caption{Hoverable and clickable course mention in the \emph{Prerequisites} field of a course} \label{fig:sk-hover}
\end{figure}

@@

With an active schedule still in use, students often want to plan their next semester's schedule. This is impossible with the Better CDCS extension, which instead adds courses from both terms to the same schedule, sometimes causing non-existent conflicts. A CDCS user must clear their entire schedule out before scheduling a new one. On Skedge, however, when a user adds a section of a term for which they do not yet have a schedule, a new one will automatically be created for that term. Users are also able to access their old schedules.

Additionally, a common feature request for Skedge is the implementation of multiple schedules \emph{per} term, allowing users to experiment with different schedule possibilities.\footnote{Currently under development, but simple to implement given the existing schedule management structure.}

@@

\subsubsection{Unified Search (left side)}

@@

\subsubsection{Skedge DSQL (right side)}
